|

### 2020-04-05 paper.Rmd
Took out plotly/orca.
Needs complicated installation...

---
title: |
  |
  | 
  | \vspace{1cm}Writing a reproducible paper
  | in R Markdown*^[*Corresponding address: mail@paulcbauer.eu. Acknowledgments: I am grateful to all those generous people that invest their time into open-source software.]\vspace{0.5cm}
  |
author: |
  | Paul C. Bauer
  | Mannheim Centre for European Social Research
date: |
  |       
  |
  | `r gsub("^0", "", format(Sys.time(), "%d %B, %Y"))`
  |
  | Feedback? 
  | mail@paulcbauer.eu
  |
linestretch: 1.2
colorlinks: true
abstract: \noindent\setstretch{1}The present paper provides a template for a reproducible scientific paper written in R Markdown. Below I outline some of the "tricks"/code (e.g., referencing tables, sections etc.) I had to figure out to produce this document. The underlying files which produce this document can be downloaded [here](https://drive.google.com/drive/folders/1zJP3cNPrHN-gj0rcmbHQgg-XA0hqDXdd?usp=sharing). I think I got pretty far but there is always room for improvement and more automatization, in parallel to the incredible developments in R and Rstudio (bookdown etc.). I intend to update this file when I discover more convenient code.\vspace{.8cm}
bibliography: references.bib
csl: american-sociological-association.csl
output:
  bookdown::pdf_document2:
    includes:
      in_header: header.tex
    toc: no
    keep_tex: true
mainfont: Times New Roman
sansfont: Times New Roman
fontsize: 12pt
link-citations: true
documentclass: article
geometry: margin=1in
always_allow_html: yes
header-includes:
   - \usepackage{dcolumn}
   - \usepackage{color}
---

@@

I would recommend to use the command below and copy/paste the output into the first R chunk in your `paper.rmd` file. Normally we would do this when we compile/generate the paper for the last time. For more advanced tools see [packrat](https://rstudio.github.io/packrat/).

```{r fig-versioning, echo=TRUE}
cat(paste("#", capture.output(sessionInfo()), "\n", collapse ="")) 
  # or use message() instead of cat()
```

@@

## Plotly graphs
Plotly is a popular graph engine that let's you also produce interactive graphs that you can embed in html webpages or documents (e.g., see [here](https://paulcbauer.shinyapps.io/visualizing-causal-scenarios/)). I am a big fan. For some time there was no easy, automatic way to insert high resolution Plotly graphs into your R Markdown PDF. However, this changed since Plotly provided Orca, a command line application for generating static images from Plotly graphs. The installation is a bit tricky (see here: https://github.com/plotly/orca#installation) but once you get it running you can produce beautiful graphs and include them in your RMarkdown PDF using some simple latex as shown below in Figure \@ref(fig:fig-3). Potentially, in case you did not install the command line application this part may fail. If so simply exclude the chunk and the latex code.

```{r fig-3, message=FALSE, warning=FALSE}
library(plotly)
p <- plot_ly(cars, type = "scatter", mode="markers",
        x=~speed, 
        y=~dist)
Sys.setenv('MAPBOX_TOKEN' = '12423423') # set arbitrary token
orca(p, "plotly-plot.pdf")
```

\begin{figure}[H]
\centering
\caption{An plotly plot that was exported as PDF with orca before}\label{fig:fig-3}
		\includegraphics[width=0.9\linewidth]{plotly-plot.pdf}
\begin{flushleft}
\end{flushleft}
\end{figure}
\vspace{-1.2cm}

@@

>>>>

---
title: |
  |
  | 
  | \vspace{1cm}Writing a reproducible paper
  | in R Markdown*^[*Corresponding address: mail@paulcbauer.eu. Acknowledgments: I am grateful to all those generous people that invest their time into open-source software.]\vspace{0.5cm}
  |
author: |
  | Paul C. Bauer
  | Mannheim Centre for European Social Research
date: |
  |       
  |
  | `r gsub("^0", "", format(Sys.time(), "%d %B, %Y"))`
  |
  | Feedback? 
  | mail@paulcbauer.eu
  |
linestretch: 1.2
colorlinks: true
abstract: \noindent\setstretch{1}The present paper provides a template for a reproducible scientific paper written in R Markdown. Below I outline some of the "tricks"/code (e.g., referencing tables, sections etc.) I had to figure out to produce this document. The underlying files which produce this document can be downloaded [here](https://drive.google.com/drive/folders/1zJP3cNPrHN-gj0rcmbHQgg-XA0hqDXdd?usp=sharing). I think I got pretty far but there is always room for improvement and more automatization, in parallel to the incredible developments in R and Rstudio (bookdown etc.). I intend to update this file when I discover more convenient code.\vspace{.8cm}
bibliography: references.bib
csl: american-sociological-association.csl
output:
  bookdown::pdf_document2:
    includes:
      in_header: header.tex
    toc: no
    keep_tex: true
mainfont: Times New Roman
sansfont: Times New Roman
fontsize: 12pt
link-citations: true
documentclass: article
geometry: margin=1in
always_allow_html: yes
---

@@

I would recommend to use the command below and simply add it to the appendix as I did here in Appendix \@ref(sec:rsessioninfo). This will make sure you always provide the package versions that you used in the last compilation of your paper. For more advanced tools see [packrat](https://rstudio.github.io/packrat/).

```{r fig-versioning, echo=TRUE, eval=FALSE}
cat(paste("#", capture.output(sessionInfo()), "\n", collapse ="")) 
  # or use message() instead of cat()
```

@@

@@

## Attach R session info in appendix {#sec:rsessioninfo}

Since R and R packages are constantly evolving you might want to add the R session info that contains information on the R version as well as the packages that are loaded.

```{r echo=FALSE}
print(sessionInfo(), local = FALSE)
```
